# Attendance {#sec-attendance}

```{r setup, include=FALSE}
# FUNCTIONS AND LIBRARIES
# have to load all data over again each document https://forum.posit.co/t/quarto-cant-find-r-objects/156848
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)    #for plots
library(partykit)   # for decision tree statistical analysis
library(tidyverse)  #for data munging including dates
library(viridis)    #color scheme

attendance <- read.csv("raw_data/processed_attendance_named.csv")
# read.csv("raw_data/processed_last_two_years_attendance.csv")
# read.csv("raw_data/processed_joined_post.csv")
# read.csv("raw_data/processed_postworkshopsurveys_named.csv")
```

## Executive summary

**Counts of workshop attendance are only influenced by whether a workshop was presented as part of course instruction.** Format (virtual, in-person, hybrid) and marketing did not change attendance counts. Even topics (@sec-topics) didn't impact attendance counts.

\newpage

## Per-workshop attendance by format and request

### Statistical analysis

For scheduled workshops, format and year impact attendance numbers in a conditional inference tree analysis.  Virtual and hybrid workshops get generally higher numbers.  Within in-person workshops, the most recent two years (2023-2024) have lowest numbers attending per workshop. 

-   format (in person vs virtual vs hybrid)

-   calendar year (starts in January)

-   semester (spring, summer, or fall)

-   workshop topic

-   multi-day vs single day scheduling

```{r att_tree, echo=FALSE, message = FALSE, warning = FALSE, output = FALSE}
library(ggplot2)    #for plots
library(partykit)    #for ctree
this_year <- format(as.Date(Sys.Date(), format="%Y/%m/%d/"),"%Y")
last_two_years <- as.numeric(this_year)-2
att_tree <- ctree(Total.Attendees ~ 
                    as.factor(Format) +
                    as.factor(year)+
                    as.factor(WorkshopCode) + 
                    as.factor(Is.this.visit.part.of.a.series.) +
                    as.factor(Semester),
                   # hour,
                  data = attendance [
                    attendance$Is.Course == "Not a course" &
                      attendance$Requested. == "No"&
                      attendance$year <= this_year &
                      attendance$year >= last_two_years,]
                  )

plot(att_tree)
#print(paste("Workshops from", last_two_years, "to", this_year, "(last two calendar years)"))
```

When we examine all workshops (included on-request visits to classes and on-request workshops), we add the following variables:

-   workshop was in a course

-   requested or not

Whether a workshop was in a course (where students are presumably required to attend) was the most dramatic factor in increased attendance numbers. For workshops not in a course, virtual and hybrid workshops have the highest attendance.

```{r att_tree2, echo=FALSE, message = FALSE, warning = FALSE}
att_tree2 <- ctree(Total.Attendees ~ 
                    as.factor(Format) +
                    as.factor(year)+
                    as.factor(WorkshopCode) + 
                    as.factor(Is.this.visit.part.of.a.series.)+
                    as.factor(Semester) +
                    # hour +
                    as.factor(Is.Course) +
                    as.factor(Requested.)
                  ,
                  data = attendance[
                      attendance$year <= this_year &
                      attendance$year >= last_two_years,]
                  )

plot(att_tree2)
```

### Format

Ignoring all other factors, the workshop format was not significantly different. You can also see this with a different visual analysis using notched box plots. The overlapping "notches" here show that there is no difference between median attendance for scheduled (not on request, not in a class) workshops by format.

```{r attendance_by_format_request, echo=FALSE, message = FALSE, warning = FALSE}
attendance[attendance$Is.Course == "Not a course" &
                             attendance$Requested. == "No",]%>%
  ggplot(mapping = aes(x = Format,
                       y = Total.Attendees))+
  geom_boxplot(notch = TRUE) + 
  labs(x = "Workshop format",
         y = "Total attendees per workshop"
         )


```

### Workshop attendance over time

The median number of people at each scheduled workshop has declined slightly per calendar year from 2021-2024. Workshop attendance at courses is higher, presumably because most classes have to reach a certain enrollment to "make".

```{r avg_attendance_over_time, echo=FALSE, message = FALSE, warning = FALSE}
plot_time <- attendance %>% 
  ggplot(mapping = aes(x = as.factor(year),
                       y = Total.Attendees,
                       fill = Is.Course)) +
  geom_boxplot(notch = TRUE) +
  labs (y = "Total attendees per workshop",
        x = "Calendar year",
        fill = "Workshop offered in course")
plot_time
```


## Total people reached

The total number of people reached has no strong trends since 2021.

```{r, total_reached_over_time, echo=FALSE, message = FALSE, warning = FALSE}

attendance %>%
  group_by(year, Is.Course) %>%
  summarize(total_reached = sum(Total.Attendees, na.rm = TRUE)) %>%
  bind_rows(summarise(.,
                      across(where(is.numeric), sum),
                      across(where(is.character), ~"Total")))%>% # https://stackoverflow.com/a/50322272
  pivot_wider(names_from =  year,
              values_from = total_reached)
  
```

The proportion of total people reached each calendar year in courses peaked in 2020, declined, and then has increased each calendar year since 2021.

```{r, prop_attendance_over_time, echo=FALSE, message = FALSE, warning = FALSE}
# https://r-graphics.org/recipe-bar-graph-proportional-stacked-bar
attendance %>%
  group_by(year,
           Is.Course) %>%
  summarize(count_per_each = n()) %>%
ggplot(
       aes(x = year,
           y = count_per_each,
           fill = Is.Course)) +
  geom_col(position = "fill")+
    scale_fill_viridis_d (aesthetics = "fill")+
  labs(y = "Proportion of people reached",
       x = "Calendar year",
       fill = "Workshop offered in course")


```

\newpage

::: content-hidden
## Workshop length vs attendance

### length of session

-   Low priority: session length vs attendance

### Single day over multiple sessions vs two-day workshops

```{r carpentries_attendance, echo=FALSE, message = FALSE, warning = FALSE}
# #Last one! Plotting attendance for carpentries by multi-day VS single-topic
# 
# carpentries <- workshop %>% filter(grepl('Standalone Bash|Standalone Carpentries R|Standalone Git|
#                                               Standalone Openrefine|Standalone Python|Standalone SQL|Two-day Carpentries with R|Two-day Carpentries with Python', Topic))
# 
# carpentries %>%
#   ggplot (aes(x=Topic, y=Total.Attendees, fill=Topic)) +
#   geom_boxplot(outlier.shape = NA) +
#   scale_fill_viridis(discrete = TRUE) +
#   theme(panel.background = element_rect(fill = "lightgray",
#                                         color = "white",
#                                         size = 0.5, linetype = "solid"),
#         panel.grid.major = element_line(size = 0.5, linetype = "solid",
#                                         color = "darkgray"),
#         panel.grid.minor = element_line(size = 0.25, linetype = "solid",
#                                         color = "darkgray"),
#         plot.title = element_text(size = 20, hjust = 0.5),
#         axis.title = element_text(size = 14),
#         axis.text = element_text(size = 12, angle = 90, hjust = 0.95, vjust = 0.2)
#   )+
#   geom_jitter(alpha = 0.55, size = 4, position = position_jitter (width = .08, height = .04), show.legend = FALSE) +
#   ggtitle('Multi-Day VS Single Day Workshops')


```

## Workshop helper load for on-request workshops over time

DSI request 2023/07: - TODO: Libraries personnel to attendance ratios for On Request workshops. which high-helper topics requested more over time and do we have enough data yet, are those increasing.

```{r attendance_over_time, echo=FALSE, message = FALSE, warning = FALSE}
 # plot_helpers <- attendance[attendance$Requested.=="Y",] %>%
 #   ggplot(mapping = aes(x = as.factor(Calendar.Year),
 #                        y = helpers/Total.Attendees,
 #                        fill = Topic)) +
 #   geom_boxplot(notch = TRUE)
 # plot_helpers
```

\newpage
:::
