# Offerings {#sec-offerings}

```{r setup, include=FALSE}
# FUNCTIONS AND LIBRARIES
# have to load all data over again each document https://forum.posit.co/t/quarto-cant-find-r-objects/156848
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)    #for plots
library(tidyverse)  #for data munging including dates
library(viridis)    #color scheme


attendance_named <- read.csv("raw_data/processed_attendance_named.csv")

```

The number of distinct topics has declined since 2022, likely due to loss of digital scholarship specialist expertise.
```{r workshop_descriptive_stats_topics_unique, echo=FALSE, message = FALSE, warning = FALSE}
topics_desc <- attendance_named %>%
  group_by(year,
           Semester,
           Is.Course,
           Requested.
      ) %>%
  summarize(topics_count = n_distinct(WorkshopCode))


ggplot(data = topics_desc,
       mapping = aes(x = year,
                     y = topics_count))+
  geom_bar(stat = "identity")+
  labs(x = "Calendar year",
       y = "Number of unique topics offered")

```


While we offer many scheduled workshops each semester (upper left panel, "Not requested/Regularly scheduled"), we continue to increase our course-based "workshops on request" visits (lower right panel) as well as a low but steady number of out-of-class requested workshops (upper right panel).

```{r joined_post, echo=FALSE, message = FALSE, warning = FALSE}

to_string <- as_labeller(c(`N` = "Regularly Scheduled", `Y` = "Requested"))

ggplot(data = attendance_named,
       mapping = aes(x = year,
                     fill = Is.Course))+
  geom_bar()+
  facet_grid(Is.Course ~ Requested.)+
  labs(x = "Calendar year",
       y = "Number of workshops offered",
       fill = "Within a course")
```



::: {.content-hidden}

We have increased the number of topics we've brought "on request" to groups and courses.

```{r workshop_descriptive_stats_topics, echo=FALSE, message = FALSE, warning = FALSE}
topics_desc <- attendance_named %>%
  group_by(year,
           Semester,
           Is.Course,
           Requested.
      ) %>%
  summarize(topics_count = n_distinct(WorkshopCode))


ggplot(data = topics_desc,
       mapping = aes(x = year,
                     y = topics_count,
                     fill = Is.Course))+
  geom_bar(stat = "identity")+
  facet_grid(~Requested., labeller = to_string)+
  labs(x = "Calendar year",
       y = "Number of unique topics offered",
       fill = "Within a course")

```

LATER TODO: How many instructors and helpers per semester
  - BN gather number of helpers from Libraries collaborators + internal notes.  later in report will cover helper to attendee ratio.
  - 11/28/2023 requested BN to request MB to add external helper count.  DONE but need to backfill data from notes.
  
  
:::
