# Descriptive numbers

While we offer many scheduled workshops each semester, we continue to increase our course-based "workshops on request" (right panel).  This has resulted in an incrase in proportion of people we reach each time period to be weighted towards course visits (@sec-attendance)

```{r setup, include=FALSE}
# FUNCTIONS AND LIBRARIES
# have to load all data over again each document https://forum.posit.co/t/quarto-cant-find-r-objects/156848
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)    #for plots
library(tidyverse)  #for data munging including dates
library(viridis)    #color scheme


attendance_named <- read.csv("raw_data/processed_attendance_named.csv")

```


```{r joined_post, echo=FALSE, message = FALSE, warning = FALSE}

ggplot(data = attendance_named,
       mapping = aes(x = year,
                     fill = Is.Course))+
  geom_bar()+
  facet_grid(~Requested.)+
  labs(y = "Number of workshops offered")
```


We have increased the number of topics we've brought "on request" to groups and courses.  The number of distinct topics has declined in the last academic year, likely due to loss of specialist expertise with staff loss.

```{r workshop_descriptive_stats_topics, echo=FALSE, message = FALSE, warning = FALSE}
topics_desc <- attendance_named %>%
  group_by(year,
           Semester,
           Is.Course,
           Requested.
      ) %>%
  summarize(topics_count = n_distinct(WorkshopCode))

topics_desc

ggplot(data = topics_desc,
       mapping = aes(x = year,
                     y = topics_count,
                     fill = Is.Course))+
  geom_bar(stat = "identity")+
  facet_grid(~Requested., labeller = label_both)+
  labs(y = "Number of unique topics offered")

```

LATER TODO: How many instructors and helpers per semester
  - BN gather number of helpers from Libraries collaborators + internal notes.  later in report will cover helper to attendee ratio.
  - 11/28/2023 requested BN to request MB to add external helper count
