# Concepts of Data-Driven Visualization

The materials for this workshop are available in [OSF]() and [GitHub]().


```{r setup, include=FALSE}
# FUNCTIONS AND LIBRARIES
# have to load all data over again each document https://forum.posit.co/t/quarto-cant-find-r-objects/156848
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)    #for plots
library(tidyverse)  #for data munging including dates
library(viridis)    #color scheme


attendance_named <- read.csv("raw_data/processed_attendance_named.csv")

```

## Descriptive numbers
This section shows who is teaching the workshop and whether their sessions are in or out of a course.

```{r}

attendance_named %>%
  dplyr::filter(WorkshopCode == "VIZ101") %>%
  dplyr::count(Entered.By, Is.Course)

```

## Attendance in scheduled workshops

### By Timing

There are no obvious trends based on time of day or weekday with the current sample size.  In-class workshops do not record time of day and thus are not included.

```{r}

plot_time <- attendance_named %>% 
  dplyr::filter(WorkshopCode == "VIZ101" & hour != 0) %>%
  ggplot(mapping = aes(x = hour,
                       y = Total.Attendees,
                       color = Is.Course,
                       shape = Is.Course)) +
  geom_point() +
  labs (y = "Total attendees per workshop",
        x = "Hour of day (24 hr scale)",
        fill = "Workshop offered in course") +
  facet_wrap(~wday)
plot_time


```

### By semester and year

This workshop is offered in both spring and fall semesters. More attendees come to in-class offerings.

```{r, echo = FALSE, warning=FALSE}

plot_date <- attendance_named %>% 
  dplyr::filter(WorkshopCode == "VIZ101") %>%
  ggplot(mapping = aes(x = as.factor(year),
                       y = Total.Attendees,
                       fill = Semester)) +
  geom_boxplot(notch = TRUE) +
  labs (y = "Total attendees per workshop",
        x = "Semester",
        fill = "Workshop offered in course") +
  facet_wrap(~Is.Course)
plot_date

```

